Figures

### 2019-05-23 figures/08_exploratory_dotplot.Rmd
split mega figs

```{r dotplot, message=FALSE, echo=FALSE, warning=FALSE}
# ---- dotplot ----

@@

```{r densityplots, message=FALSE, echo=FALSE, warning=FALSE}
# ---- densityplots ----
library(ggforce)

>>>>

\pagebreak
```{r dotplot, message=FALSE, echo=FALSE, warning=FALSE}
# ---- dotplot ----

@@

\pagebreak
```{r densityplots, message=FALSE, echo=FALSE, warning=FALSE}
# ---- densityplots ----
library(ggforce)
